### 2024-01-31 README.Rmd
describe package logo (closes #512)
in general, the package is in a good spot with alt text.
transition redirecting URL

# infer R Package <img src="man/figures/logo.png" align="right" width=280 />

@@

[![R-CMD-check](https://github.com/tidymodels/infer/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/tidymodels/infer/actions/workflows/check-standard.yaml)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)
[![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/main.svg)](https://codecov.io/github/tidymodels/infer/?branch=main)

>>>>

# infer R Package <img src="man/figures/logo.png" alt="A hexagonal logo. A silhouette of a fir tree sits atop green text, reading 'infer'. The logo has a white background and green border." align="right" width=280 />

@@

[![R-CMD-check](https://github.com/tidymodels/infer/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/tidymodels/infer/actions/workflows/check-standard.yaml)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)
[![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/main.svg)](https://app.codecov.io/github/tidymodels/infer/?branch=main)
